apply flashr2 with OCV

### 2018-01-22 analysis/templateforOCV.Rmd
Files commited by wflow_commit.

call_method = function(Y_data,method,Kmax = 50){
  if(method == "flash"){
    data = flashr2::flash_set_data(Y_data)
    # f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,var_type = "constant")
    f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == "flash_wn"){
    data = flashr2::flash_set_data(Y_data)
    # f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,var_type = "constant",nullcheck=FALSE)
    f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,nullcheck=FALSE)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == "flash_bf"){
    data = flashr2::flash_set_data(Y_data)
    # f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,var_type = "constant")
    # f = flashr2::flash_backfit(data,f_greedy,var_type = "constant")
    f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax)
    f = flashr2::flash_backfit(data,f_greedy)
    Y_hat = f$EL %*% t(f$EF)
  }else if(method == "PMD"){
    res_log = capture.output({out = PMA.wrapper(Y_data,ngrids = 10,K = Kmax,fold = 10)})
    if(length(out$d)==1){
      Y_hat =  (out$d) * out$u %*% t(out$v)
    }else{
      Y_hat =  out$u %*% diag(out$d) %*% t(out$v)
    }
  }else if(method == 'PN'){
    library(ebnm)
    library(flashr2)
    data = flashr2::flash_set_data(Y_data)
    # f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,ebnm_fn = ebnm_pn,var_type = "constant")
    f_greedy = flashr2::flash_add_greedy(data,Kmax=Kmax,ebnm_fn = ebnm_pn)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == "softImpute"){
    gsoft = try(softImpute.wrapper(Y_data,ngrids = 10,K = Kmax,fold = 10))
    if(length(gsoft$d)==1){
      Y_hat =  try((gsoft$d) * gsoft$u %*% t(gsoft$v))
    }else{
      Y_hat =  try(gsoft$u %*% diag(gsoft$d) %*% t(gsoft$v))
    }
  }else{
    # stop("the method is not implemented yet, please check it out")
    Y_hat = matrix(0,ncol = dim(Y_data)[2],nrow = dim(Y_data)[1])
  }
  return(Y_hat)
}

@@

>>>>

call_method = function(Y_data,method,Kmax = 50){
  if(method == "flash"){
    data = flashr2::flash_set_data(Y_data)
    f_greedy = flashr2::flash_add_greedy(data,K=Kmax)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == "flash_wn"){
    data = flashr2::flash_set_data(Y_data)
    f_greedy = flashr2::flash_add_greedy(data,K=Kmax,nullcheck=FALSE)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == "flash_gb"){
    data = flashr2::flash_set_data(Y_data)
    f_greedy = flashr2::flash_add_greedy(data,K=Kmax)
    f = flashr2::flash_backfit(data,f_greedy)
    Y_hat = f$EL %*% t(f$EF)
  }else if(method == "flash_bf"){
    data = flashr2::flash_set_data(Y_data)
    f_data = flashr2::flash_add_factors_from_data(data,K = Kmax)
    f = flashr2::flash_backfit(data,f_data)
    Y_hat = f$EL %*% t(f$EF)
  }else if(method == "PMD"){
    res_log = capture.output({out = PMA.wrapper(Y_data,ngrids = 10,K = Kmax,fold = 10)})
    if(length(out$d)==1){
      Y_hat =  (out$d) * out$u %*% t(out$v)
    }else{
      Y_hat =  out$u %*% diag(out$d) %*% t(out$v)
    }
  }else if(method == 'PN'){
    library(ebnm)
    library(flashr2)
    data = flashr2::flash_set_data(Y_data)
    f_greedy = flashr2::flash_add_greedy(data,K=Kmax,ebnm_fn = ebnm_pn)
    Y_hat = f_greedy$EL %*% t(f_greedy$EF)
  }else if(method == 'PMD_d'){
    out = PMA::PMD(Y_data, K = Kmax)
    Y_hat =  out$u %*% diag(out$d) %*% t(out$v)
  }else if(method == 'softImpute_d'){
    gsoft = softImpute::softImpute(Y_data, rank.max = Kmax)
    Y_hat =  gsoft$u %*% diag(gsoft$d) %*% t(gsoft$v)
  }else if(method == "softImpute"){
    gsoft = try(softImpute.wrapper(Y_data,ngrids = 10,K = Kmax,fold = 10))
    if(length(gsoft$d)==1){
      Y_hat =  try((gsoft$d) * gsoft$u %*% t(gsoft$v))
    }else{
      Y_hat =  try(gsoft$u %*% diag(gsoft$d) %*% t(gsoft$v))
    }
  }else if(method == "SF_flash"){
    gsoft = try(softImpute.wrapper(Y_data,ngrids = 10,K = Kmax,fold = 10))
    LL = gsoft$u %*% diag(gsoft$d)
    FF = gsoft$v
    data = flashr2::flash_set_data(Y_data)
    f_data = flashr2::flash_add_lf(data, LL=LL, FF=FF)
    f = flashr2::flash_backfit(data,f_data)
    Y_hat = f$EL %*% t(f$EF)
  }else{
    # stop("the method is not implemented yet, please check it out")
    Y_hat = matrix(0,ncol = dim(Y_data)[2],nrow = dim(Y_data)[1])
  }
  return(Y_hat)
}

@@

labels | null check | backfitting | greedy | ebnm_ash | ebnm_pn 
------ | ---------- | ----------- | ------ | -------- | ------
flashG | yes| |yes | yes |
flashGwn | | | yes|yes |
flashB | yes| yes| | yes|
PN | yes | | yes| |yes
